A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-17 writeup/paper.tex
Updated title, abstract, author order

%
% File acl2012.tex
%
% Contact: Maggie Li (cswjli@comp.polyu.edu.hk), Michael White (mwhite@ling.osu.edu)
%%
%% Based on the style files for ACL2008 by Joakim Nivre and Noah Smith
%% and that of ACL2010 by Jing-Shin Chang and Philipp Koehn

@@

\title{Some Negativity Results for Moduli}

\author{Ellie Pavlick \\
  {\tt elliepavlick@gmail.com} \\\And
  Chris Callison-Burch \\
  {\tt ccb@cs.jhu.edu} \\\And
  Dmitry Kachaev \\
  {\tt dmitry.kachaev@gmail.com } \\}

@@

\begin{abstract}
 Let $\hat{F} < \pi$.  A central problem in elliptic model theory is the characterization of Noetherian functions.  We show that \begin{align*} Y' \left( \mathscr{{O}} \emptyset, \dots, \pi \emptyset \right) & \sim \sup \iiint_{{\eta_{\lambda,\Xi}}} t \left( \hat{Z}, \dots, \bar{h} + e \right) \,d R \\ & \ne \sum  \tilde{\Omega} \left( \| K \|^{-1}, N \wedge \pi \right) \vee \dots + L''  .\end{align*}  It would be interesting to apply the techniques of \cite{cite:0} to quasi-Gaussian vectors. This leaves open the question of uniqueness.
\end{abstract}

>>>>

@@

\title{A large scale study of the languages spoken (by bilinguals) on Mechanical Turk}
\title{The Language Demographics of  Amazon Mechanical Turk}

\author{Ellie Pavlick  \\
  \small {\tt elliepavlick@gmail.com} \normalsize \\
  \And
  Dmitry Kachaev  \\
 \small  {\tt dmitry.kachaev@gmail.com } \normalsize \\
  \And
  Chris Callison-Burch \\
 \small  {\tt ccb@seas.upenn.edu} \normalsize \\
  }

@@

\begin{abstract}
We present a large scale study of the languages spoken by bilingual workers on Mechanical Turk (MTurk).  
We establish a  methodology for determining the language skills of anonymous crowd workers that is more robust than simple surveying.  We validate workers' self-reported language skills claims by measuring their ability to correct translate words, and performing geolocation to see if they come from a country where the language is spoken. Moreover, rather than posting a one-off survey, we posted large, paid tasks consisting of 1,000 assignment to translate a total of 10,000 words in each of 100 languages.  Our study ran for weeks, and was highly visible on the MTurk crowdsourcing platform, increasing the chances that bilinguals workers would have seen.  Our study resulted in the creation of bilingual dictionaries for a wide variety of languages, and acted as census of the bilingual speakers on MTurk.  We use this to recommend languages with the largest speaker populations that are good candidates for other researchers who want to  develop crowdsourced, multilingual technologies.

\end{abstract}
